\textit{Supporting Information for}: Geometric models reveal behavioral and neural signatures of transforming experiences into memories

### 2020-10-16 paper/supplementary_information.tex
added caption for new supplemental figure, formatting edits

% \FloatBarrier
\newpage
\begin{centering}
  \vspace*{\fill}
  \section*{Supplementary figures}
    \vspace*{\fill}
  \end{centering}

\begin{figure}[tp]
\centering
\includegraphics[width=0.6\textwidth]{figs/topic_space_flow}
\caption{\small \textbf{Visualizing the consistency of flow through topic space across participants.} \textbf{A.} \textbf{B.} \textbf{C.}}
\label{fig:arrows}
\end{figure}

\newpage
\begin{centering}
  \vspace*{\fill}
    \subsection*{Participant-level figures referenced in the main text}
    \vspace*{\fill}
  \end{centering}

>>>>

% \FloatBarrier
\newpage
%\begin{centering}
%  \vspace*{\fill}
  \section*{Supplementary figures}

\newpage
\begin{figure}[tp]
\centering
%\includegraphics[width=1\textwidth]{figs/}
\caption{\small \textbf{Methods detail for recall trajectory analysis displayed in Figure~\trajectories B} \textbf{A.} This panel replicates Figure~\trajectories B in the \textit{Main text}, but with two additions.  First, individual participants' recall trajectories are displayed (faintly) as light gray lines.  Second, three locations on the trajectory have been highlighted (blue, yellow, and red circles).  \textbf{B.}  These zoomed-in views of the locations highlighted in Panel A show the average trajectory (black) and individual participants' trajectories (gray lines) that intersect the given region of topic space.  \textbf{C.} For each circular region of topic space tiling the 2D embedding plane displayed in Panel A, we compute the distribution of angles formed between each participant's trajectory segment (i.e., the point at which the trajectory enters and exists the region of topic space) and the $x$-axis.  The distributions of angles for these three example regions are displayed in the colored rose plots.  We use Rayleigh tests to assign an arrow direction, length, and color for that region of topic space.  Arrows displayed in blue are significant at the $p < 0.05$ level (corrected).  The arrow directions are oriented according to the circular means of each distribution, and the arrow lengths are proportional to the lengths of those mean vectors.  The example regions have been oriented from left to right in decreasing order of consistency across participants.}
\label{fig:arrows-methods}
\end{figure}
\vspace*{\fill}

\newpage
    \subsection*{Participant-level figures referenced in the main text}
    %\vspace*{\fill}
  %\end{centering}
